What the hell is the title of this paper?

### 2018-05-10 NIPS 2018/main.tex
Edits

Recent advances have allowed reinforcement learning (RL) \cite{}\todo{cite Sutton} to solve a wide variety complex tasks, ranging from playing Atari \cite{} and the game of Go \cite{} to the control of sophisticated robotics systems \cite{}. The main drawback is that RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks. One of the most promising solutions is transfer learning, which focuses on reusing past knowledge available to the agent in order to reduce the sample-complexity for learning new tasks. In the typical settings of transfer in RL \cite{}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution. Then, given a \textit{target task} drawn from the same distribution, or a slightly different one, the agent can rely on knowledge from the source tasks to speed-up the learning process. This constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of previously learned tasks. Several algorithms have been proposed in the literature to transfer experience samples \cite{}, policies/options \cite{}, rewards \cite{}, value functions \cite{}, features \cite{}, and so on. We refer the reader to \cite{} for a thorough survey on transfer in RL.

One of the most relevant problems in this context is how to efficiently explore the target task based on knowledge from the source tasks. Intuitively, assuming tasks in the family under consideration share some similarities due to the common distribution, much better exploration strategies than uninformed ones (e.g., $\epsilon$-greedy) can be adopted for quickly learning the target task. Appealing approaches for this problem are the Bayesian ones (e.g., \cite{}), which are able to model the uncertainty over the current task based on previous knowledge and drive exploration so that this uncertainty is reduced as quickly as possible, or the model-based ones (e.g., \cite{}), which typically transfer samples to improve the estimate of the current task model and adopt classic count-based exploration. However, we believe all this approaches to have several limitations that reduce their practical applicability.\todo{mention some}

In this work, we tackle such limitations by taking a more general approach. Similarly to \cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions. Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior. Leveraging on recent ideas from randomized value functions (\cite{}), we design a Thompson sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t. (with respect to) the sampled value function. We show that our approach is very general, in the sense that it does not require any specific choice of function approximator or prior/posterior distribution models. \todo[inline]{Maybe mention something about theory/experiments here}

>>>>

Recent advances have allowed reinforcement learning (RL) \cite{} to achieve impressive results in a wide variety of complex tasks, ranging from Atari \cite{}, to the game of Go \cite{}, to the control of sophisticated robotics systems \cite{}. The main limitation is that RL algorithms still require an enormous amount of experience samples before successfully learning such complicated tasks. One of the most promising solutions is transfer learning, which focuses on reusing past knowledge available to the agent in order to reduce the sample-complexity for learning new tasks. In the typical settings of transfer in RL \cite{}, the agent is assumed to have already solved a set of \textit{source tasks} generated from some unknown distribution. Then, given a \textit{target task} drawn from the same distribution, or a slightly different one, the agent can rely on knowledge from the source tasks to speed-up the learning process. This constitutes a significant advantage over plain RL, where the agent learns each new task from scratch independently of previously learned tasks. Several algorithms have been proposed in the literature to transfer experience samples \cite{}, policies/options \cite{}, rewards \cite{}, value functions \cite{}, features \cite{}, and so on. We refer the reader to \cite{} for a thorough survey on transfer in RL.

One of the most relevant problems in this context is how to efficiently explore the target task based on knowledge from the source tasks. Intuitively, assuming the tasks under consideration share some similarities due to the common distribution, much better exploration strategies than uninformed ones (e.g., $\epsilon$-greedy) can be adopted for quickly learning the target task. Among the appealing approaches for this problem we find Bayesian methods (e.g., \cite{}), which are able to model the uncertainty over the current task based on previous knowledge and drive exploration so that this uncertainty is reduced as quickly as possible. Similarly, model-based algorithms (e.g., \cite{}) typically transfer samples to improve their estimates of the task model and adopt classic count-based exploration to drive the agent towards regions where such estimates are more uncertain. However, all these approaches either require strong assumptions (for example, on the distribution involved in Bayesian methods) or do not scale well to large problems. This greatly limits their practical applicability.

In this work, we tackle such limitations by considering a more general approach. Similarly to \cite{}, we assume tasks to share similarities in their value functions and use the given source tasks to learn the distribution over such functions. Then, we use this distribution as a prior for learning the target task and we propose and efficient variational approximation of the corresponding posterior. Leveraging on recent ideas from randomized value functions (\cite{}), we design a Thompson sampling-based algorithm which efficiently explores the target task by repeatedly sampling from the posterior and acting greedily w.r.t. (with respect to) the sampled value function. We show that our approach is very general, in the sense that it does not require any specific choice of function approximator or prior/posterior distribution models. \todo[inline]{Maybe mention something about theory/experiments here}
